---
title: "Exercise 1"
author: "Cuc Nguyen Marcinczyk"
date: "4/14/2021"
output: html_document
toc: true
theme: united
highlight: tango
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
Sys.setenv(LANG = "en")
```

# Friend - Season 6 summary in numbers

### __(*Warning:* spoilers ahead)__

***

### Overview

From the [Wikipedia](https://en.wikipedia.org/wiki/Friends), Friends is an American television sitcom, created by David Crane and Marta Kauffman, which aired on NBC from September 22, 1994, to May 6, 2004, lasting ten seasons.[1] With an ensemble cast starring Jennifer Aniston, Courteney Cox, Lisa Kudrow, Matt LeBlanc, Matthew Perry and David Schwimmer, the show revolves around six friends in their 20s and 30s who live in Manhattan, New York City. The series was produced by Bright/Kauffman/Crane Productions, in association with Warner Bros. Television. The original executive producers were Kevin S. Bright, Kauffman, and Crane.

Rachel Green, a sheltered but friendly woman, flees her wedding day and wealthy yet unfulfilling life and finds childhood friend Monica Geller, a tightly wound but caring chef. After Rachel becomes a waitress at West Village coffee house Central Perk, she moves into Monica's apartment above Central Perk and joins Monica's group of single friends in their mid-20s: previous roommate Phoebe Buffay, an eccentric, weird masseuse; neighbor Joey Tribbiani, a dim-witted yet loyal struggling actor and womanizer; Joey's roommate Chandler Bing, a sarcastic, self-deprecating IT manager; and Monica's older brother and Chandler's college roommate Ross Geller, a sweet-natured but insecure paleontologist.

***

### Season 6 summary

The sixth season of Friends, an American sitcom created by David Crane and Marta Kauffman, premiered on NBC on September 23, 1999. Friends was produced by Bright/Kauffman/Crane Productions, in association with Warner Bros. Television. The season contains 25 episodes and concluded airing on May 18, 2000.

In the season 6 premiere, Ross and Rachel's marriage turns out to be a drunken mistake that neither remembers until the other friends mention it. Ross promises Rachel he will get them an annulment, then secretly does nothing because he cannot face having three failed marriages. By the time Rachel discovers they are still married, an annulment is impossible due to their history; they are forced to get a divorce. After ignoring the numerous signs that they should get married, Monica and Chandler decide to live together, forcing Rachel to move in with Phoebe. Joey gets a new roommate, Janine (Elle Macpherson). They develop feelings for each other and date briefly until Janine criticizes Monica and Chandler, ending the relationship. After Janine moves out, Joey struggles with paying his bills so he takes a job at Central Perk. He soon lands a role on a cable TV series called Mac and C.H.E.E.S.E., starring alongside a crime-fighting robot. Ross gets a teaching job at New York University. He dates Elizabeth (Alexandra Holden), a student, despite it being against university policy. Elizabeth's father, Paul (Bruce Willis), disapproves of Ross but falls for Rachel, and they start dating. Both relationships soon end: Elizabeth is too immature for Ross, and previously reserved Paul opens up emotionally and is more than Rachel can handle. Phoebe and Rachel's apartment catches fire, and Rachel moves in with Joey, while Phoebe stays with Chandler and Monica, though they later switch. While at a museum that has a two-year wait for weddings, Monica puts her name on the reservation list as a joke. When Chandler intercepts the museum's phone call about a cancellation, he panics; however, Chandler has been planning to propose while pretending he may never want to marry. While dining at a fancy restaurant, Chandler's planned proposal is subverted by Monica's ex-boyfriend Richard Burke, who unexpectedly shows up. Richard later tells Monica he wants to marry her and have children. Monica becomes upset at Chandler, believing his ruse about not wanting to marry. Chandler believes Monica has left him until he comes home to find their apartment decorated with candles and her waiting to propose to him. When she becomes too emotional to continue, Chandler proposes and she accepts.

***

You can see how the viewership of the episodes changed in Figure 1.

```{r viewers_plot}
episode <- seq(1,25,1)
viewer <- c(27.8, 23, 21.6, 21.1, 22.4, 23.6, 22.8, 22.1, 19.2, 18.5, 22.4, 22.3, 22.3, 24.1, 23.8, 25.9, 22.1, 20.5, 21.5, 23,  18.8, 20.6, 20, 20.9, 30.7)

viewership <- data.frame(episode, viewer)
plot(viewership, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

***

Finally, the episodes with the above-average viewership were:

| No. in season 6 | Title  | Directed by  |
|:------        |:-----: |:------:      |
| 1             | "The One After Vegas"  | Kevin S. Bright      |
| 2             | "The One Where Ross Hugs Rachel" | Gail Mancuso      |
| 3             | "The One with Ross's Denial" | Gary Halvorson      |
| 4            | "The One Where Joey Loses His Insurance" | Gary Halvorson     |
